Context Aware Virtual Assistant with Case-Based Conflict Resolution in Multi-User Smart Home Environment

### 2018-01-24 Paper/Paper.tex
Update of Paper

        In this work we will examine and develop a Virtual Assistant which is the intelligence system that is used as a control
        interface of the Smart Home environment in the Farm Side Middlesex University laboratory. Specifically, the system is
        constructed to give multiple users ability to control devices` statuses by voice or text commands through the dialogue
        interface. Primarily, the main purpose of the system is to create user friendly interface with conflict resolution based
        on user cases. As a result, a Case-Based Reasoning algorithm was created with a k-Nearest Neighbor classification algorithm.

@@

        Moreover, the user friendly graphical web interface was developed. Further, a set of randomised double-blinded
        evaluation tests were established to check procedure of smart home control actions by multiple users.

@@

    Managing a comfortable life could be a challenging task for people with special needs because some of them may need additional
    assistance to control electronic and electric devices in the living are [1]. The next group of users that probably seek
    assistance in Activities of Daily Life (ADL) is younger population while adults are away from home [1]. As a result,
    the Smart Home environments are developed to help users in controlling home and devices states with voice graphical
    interfaces [10] that are often called Virtual Assistants [1] or monitor behaviours of people
    with special needs [17] to classify changes in ADL that then alarm or notify relatives, health and care professionals
    and organizations [9]. Additional finding identified other techniques in the state of art.

@@

    perform context recognition [14] or visual tools for creating personal preferences table of each user based on semantics
    metadata [11]. As a consequence, majority of the researches is aimed to develop systems that helps alone living users.\\

@@

    needs and priorities. Some researchers in order to solve this dilemma developed context-aware automation platforms
    [13, 16] that resolves conflicts between automated devices such as fire alarms and automated door locks.

@@

    developers are focused on preference Rule-Based Reasoning (RBR) to resolve conflicts between users [1]. Even through

@@

    To sum up
    state of art, there are number of systems that monitors and adapts to single users, resolves conflicts between devices
    in single user multi-agent environments and resolves conflicts between users based on if-else rules. On the contrary,
    there is a lack of the Virtual Assistants with an adaptive conflict resolution systems.\\

@@

    voice and text based dialogue graphical web user interface for multiple users. As a result, we developed number of
    subsystems to fully implement number of requests. First of all, interaction with the VA has to be user-friendly and
    natural as a human to human interaction. Second, the system has to be able to control and monitor state of the Smart
    Home devices. Finally, the VA has to manage to resolve conflicts between multiple users, and adapt to the new user cases.\\
    To cover all objectives, we introduced and developed the VA with next modules. Firstly, we have developed user friendly
    graphical interface based on web and cloud technologies to give to user intuitive way of interacting with the VA. For this
    reason, we used dynamic web framework, cloud voice recognition and generation technologies and animated emotional icons
    to mimicry natural face emotions in the dialogues. In addition to user friendly interface, we have developed and implemented
    adaptive natural language classification algorithms based on Artificial Neural Network (ANN) to make the VA understand
    different variates of the user commands and argumentation sentences, because they are effective algorithms for
    sentence classification [19]. Therefore, users were able to speak to
    VA in the way they speak with other human. Secondly, we used Farm Side Middlesex University Smart Home laboratory and
    Smart Home devices control unit to manage and monitor Smart Home devices. In order that, we have developed and integrated
    software API to implement communication between Smart Home control unit and VA. The last but not the least, we have
    introduced and developed a conflict resolution system that used Case-Based Reasoning (CBR) to make a decision about
    conflict between multiple users. In order to make decision, VA identifies in dialogue form the argumentation of the user
    in performing an action, analyzes via k-nearest neighbour (kNN) algorithm similarities between
    this case and previous cases and chooses best-fit case [4,7,15]. In other words, VA asks user to say why he or she wants to change
    device status if there conflicting instruction from other user and makes decision what to do with device based on users
    arguments and previous cases. Futhermore, arguments priorities was established by personal user preferences [3] because
    expectations [5].\\
    Furthermore, we have established randomized double-blinded evaluation tests. In order to perform randomized double
    blinded experiment, we developed scenario creating sub-module. Firstly, it creates random scenario for tester by choosing
    conflicting device and arguments for tester by using crypto-secure randomise function based on operation system inner
    clocks. Secondly, it provides such instructions to testers that he or she was
    asked to provide command and arguments in their own words. As a result, it was hidden from us and testers scenarios till
    the beginning of the experiment. In addition, testers were asked to fill evaluation form. To conclude, feedback from
    testers are positive and only weak place of the system is accent recognition task.\\
    This paper presents Virtual Assistant in the multiple user Smart Home environment. The Virtual Assistant was created
    to manage and monitor Smart Home environment by dialogue based interaction with users. Different machine learning
    algorithms and cloud technologies were implemented to meet project objectives. The main focus of the research was to
    develop adaptive conflict resolution system based on Case-Based Reasoner. The validation tests feedback is positive.
    a case to the database of Case-Based Reasoner.\\
    This paper presents Virtual Assistant in the multiple user Smart Home environment. The architecture of the system is

@@

    our results and validation. Finally, Section V draws the conclusion and predictions for the future work.

@@

    \subsection{Overall}

@@

    The interface of the system is graphical web interface developed as web site.
    As a result, Graphical User Interface (GUI) is expressed by 3 functional and Login Pages that are listed below:
        \item Login Page: Welcome interface - user chooses his or her account.
        \item Control Page: Dialogue interface - user communicates with system in form of dialogue by voice or text chat,
        gives orders \footnote{Order is command of the user given to the system. For example, turn off the light.} and reasons \footnote{Reason is argument given by the user to the system to justify his/her order. For example, turn off the light, because my eyes hurts.}.
        \item Rules \footnote{Rule is set of instructions given for system to do automatically. For example, system is obligated keep kettle turned off from 11:00 till 13:00 everyday because of energy saving issue.}
        Page: Rules editing interface - user edits list of instructions \footnote{Rules are discussed in the Section III.} given to the system.
        \item Preferences \footnote{Preference is set of issues that justifies orders of the user to the system. Every user type has its own priority level for preferences.} Page: Preferences editing interface - user edits his or her preferences \footnote{Preferences are discussed in the Section III.}.
    Flask Micro Web Framework is used as Front End controlling technology or Back End of the interface, because most of the project is coded by Python 3 language.

@@

    As a result, the system sends record of the user input to W3C API and it returns text that is the recognition of the record.

@@

    The modules of the Speech Generation and Speech Recognition are inserted to the Dialogue component with Dilague Manager module.

@@

    \subsection{Dialogue Manager}
    Based on the data from Rule-Based Reasoner and actions done by the system it sends human readable report or response to user via interface.
    In addition to Cloud API, Dialogue Manager is part of the Dialogue component that is the subsystem to communicate with user in natural way.
    Lastly, Dialogue Manager is set of if-else rules and dialogues database developed to pretend human-like speaking.
    \subsection{Classification Component}

@@

    Text classification is non-trivial complex task that is cannot be solved sequentially or by sequential algorithms artificial neural network systems (ANN) provides the better solution \cite{14}.
    Backpropagation as an ANS is very useful in recognizing complex patterns and performing nontrivial mapping functions.
    The figure below represents a simple Feed Forward Neural Network (FNN) diagram.
    The rounded objects represent the artificial neurons or processing elements of a neural network.
    The directed lines that are connecting the neurons are called weights that are the multiplication coefficients for input signal.
    Also every line of processing elements is a layer of a network.

@@

    \subsubsection{Topology of the Artificial Neural Network} is consists of Input, Output and Hidden layers.\\

@@

    As a result, it followed by a squashing nonlinearity
    While training the ANN (see below) it was concluded that the accuracy of the neural network does not significantly changes between one hidden layer neural network and multiple hidden layer neural network.
    The most efficient number of hidden layer neurons (14) was found by calculation of the delta that was calculated by 1000 iterations of Backpropogation training algorithm with standard training/test set especially created for this experiment.
        \includegraphics[width=0.8\textwidth]{HL.png}
        \caption[]{Iterations of FNN with different Hidden Layer size, where horizontal line is number of neurons and vertical line is delta function percentage}
    \subsubsection{General Case: Trivial Reason.}

@@

    The system normally does not accept any classification lower that 80\% possibility, and if user says something not
    correlated to the predefined preferences, the system will skip classification and ask again.

@@

        User input is: \em I need to finish my project about flu \em \\
        System classified it as: \em [['Work', 0.99951473383654765], ['Health', 0.056650409249493161], ['Entertainment', 0.0011293354032656073], ['Energy', 1.4169164768812246e-05], ['Security', 1.238332260956378e-05], ['Food', 3.1674436013529605e-07]] \em

@@

    \subsubsection{General Case: Nontrivial Reason.}
    In the next example user typed "G'ylym janyp turg'an s'yraq" (Kazakh Language: Science is a burning candle).
    The system did not managed to classify this reason, because the system is tuned only for English.
        User input is: \em G'ylym janyp turg`an s`yraq \em\\
        System classified it as: \em [] (Null) \em
    \subsection{Training of FNN}
    It was used Backpropogation method for artificial neural network weights of the synapses optimisation.

@@

    In order to train neural network, a set of training documents and a specification of the pre-defined categories the documents belong to are required.

@@

    The training examples in the training set are then presented to the neural network classifier in random order, and the connection weights are adjusted according to the Backpropagation learning rule.
    This process is repeated until the learning error falls below a predefined tolerance level (99.95\%).
    Below there is an example of the training of the Reason Classifier.
        Input matrix: 260x198 Output matrix: 1x6\\
        delta after 10000 iterations:0.00195103818538\\
        delta after 20000 iterations:0.00132469839464\\
        delta after 30000 iterations:0.00105975676227\\
        delta after 40000 iterations:0.000905619354028\\
        delta after 50000 iterations:0.000802125845806\\
        delta after 60000 iterations:0.000726645045015\\
        delta after 70000 iterations:0.000668536139359\\
        delta after 80000 iterations:0.000622059862315\\
        delta after 90000 iterations:0.000583815748815\\
        delta after 100000 iterations:0.000551645861196\\
        saved synapses to: ./include/synapses.json\\
        processing time: 103.20042490959167 seconds\\
    \subsection{Rule-Based Reasoner}

@@

    Core of the Rule-Based Reasoner is the set of if-else rules:
        \item If status of device equals to status that user already wants: return similarity response; else: go further.
        \item If there is conflict between rule and user`s order: send task to Case-Based Reasoner; else: send command to Device COntrol Unit.
    \subsection{Case-Based Reasoner}
    Case-Based Reasoner works by finding the lowest distance of input case to the cases inside the database.

@@

@@

    CBR is based on a suggestion that the similar cases have similar solution.
    The decisions in our system is binary (0 for not change device status, 1 for change it).
    As a result, it is accessible that CBR assumption works in our system.

@@

    In our case inputs to the system are in different system of measurements.

@@

    As a result, standard Euclidean Distance cannot be used as a distance measurement algorithm.

@@

    Using of Mahalanobis distance significantly increases kNN accuracy.
    In addition, there was used a Genetic Algorithm to find best value of Mahalanobis covariance matrix.
    It is was set nearly 11 quadrillion types of mutations patterns.
    The covariance matrix was used as genome of each genome in the epoch.
    As a result, each epoch system chooses best accuracy model and mutates it`s one hundred children with different not significant mutations in the genome.
    Then the system iterate again while accuracy of the best model (king) will not reach threshold value.
    \subsection{Device Control Unit}

@@

    In consequence, we developed API to communicate with it.
    Vera Secure system has own web interface.
    In order to communicate with it, we sending and receiving GET and POST requests.
    Special POST requests changes status of the devices, which are kettle and light in our experiment.
    Next, updating information about device statuses is done by parsing response from special GET request sent to the Vera Secure server.

@@

    \subsection{Terminology}
    We used user types and preference system proposed by \cite{9} .
    As a result, different group of users were outlined and divided by age.
    Moreover, we declared updated system of preferences.

    \subsection{Regular Case}
    \subsection{Conflicting Case}
    \section{Results and Validation}
    %
    \section{Conclution}
    \section{References}
    \begin{thebibliography}{1}
        \bibitem {1}
        Alirezaie, M., Renoux, J., Köckemann, U., Kristoffersson, A., Karlsson, L., Blomqvist, E., Tsiftes, N., Voigt, T., Loutfi, A.: An Ontology-based Context-aware System for Smart Homes: E-care@home. Sensors. 17, 1586 (2017).

@@

        \bibitem {4}
        Göynügür, E., Bernardini, S., de Mel, G., Talamadupula, K., Şensoy, M.: Policy Conflict Resolution in IoT via Planning. Advances in Artificial Intelligence. 169-175 (2017).

@@

        \bibitem {16}
        Siolas, G., Caridakis, G., Mylonas, P., Kollias, S., Stafylopatis, A.: Context-Aware User Modeling and Semantic Interoperability in Smart Home Environments. 2013 8th International Workshop on Semantic and Social Media Adaptation and Personalization. (2013).

>>>>

        In this work we will examine and develop a Virtual Assistant that is used as a control
        interface of the Smart Home environment in the Farm Side Middlesex University laboratory.
        Specifically, the system is
        constructed to give multiple users ability to control devices by voice or text commands through the dialogue
        interface.
        Primarily, the main purpose of the research is to create user friendly interface with adaptive context aware
        Case-Based conflict resolution system.

@@

        Further, a set of randomised double-blinded
        evaluation tests were established.

@@

    Managing a comfortable Activities of Daily Life (ADL) could be a challenging task for people with special needs
    and younger population \cite{9}.
    As a result,
    the Smart Home environments are developed to help users in controlling devices \cite{13}
    that are often called Virtual Assistants \cite{9} or monitor behaviours of people
    with special needs \cite{3} to classify changes in ADL that then alarm or notify relatives, health and care professionals
    and organizations \cite{15}.
    Additional finding identified other techniques in the state of art.

@@

    perform context recognition \cite{1} or visual tools for creating personal preferences table of each user based on semantics
    metadata \cite{8}.
    As a consequence, majority of the researches is aimed to develop systems that helps alone living users.\\
    On the other hand, conflicting orders inside the system by different users can lead to the risks \cite{5}.

@@

    needs and priorities.
    Some researchers in order to solve this dilemma developed context-aware automation platforms
    \cite{5,6} that resolves conflicts between automated devices such as fire alarms and automated door locks.

@@

    developers are focused on preference Rule-Based Reasoning (RBR) to resolve conflicts between users \cite{9}. Even through

@@

@@

    voice and text based dialogue graphical web user interface for multiple users and resolve conflicts in changing environment.\\
    This paper presents Virtual Assistant in the multiple user Smart Home environment.
    The architecture of the system is

@@

    our results and validation.
    Finally, Section V draws the conclusion and predictions for the future work.

@@

    We have used updated user types and preference system proposed by \cite{9}.
    Moreover, arguments priorities was established by personal user preferences \cite{11} because
    expectations \cite{10}.\\
    The preferences are reasons why user wants to change the device status.
    Introducing reason is the way to increase usability of the system through the implicit interpretation of user needs.
    Context awareness of the system is the key for creating high usability via making the interaction
    between user and system more natural \cite{7}.\\
    We have used "Ceteris paribus" preferences binary tree representation.
    At the moment, CP-nets are most effective qualitative approach for presenting preferences in the strict known
    environment as the Smart Home \cite{10}.

@@

    The interface of the system is graphical web interface developed as web site shown in the figure below.
    Graphical User Interface (GUI) is expressed by 3 functional and Login pages.
    In the Login Page user chooses account.
    User communicates with system in form of dialogue by voice or text chat,
    gives orders \footnote{Order is command of the user given to the system.
    For example, turn off the light.} and reasons \footnote{Reason is argument given by the user to the system to
    justify his/her order.
    For example, turn off the light, because my eyes hurts.} in the Control Page.
    Rules Page and Preference Page are database table editing pages where user changes rules \footnote{Rule is set of instructions given for system to do automatically.
    For example, system is obligated keep kettle turned off from 11:00 till 13:00 everyday because of energy saving issue.} and preferences.\\
        \includegraphics[width=\textwidth]{mockup.png}
        \caption[]{Control Page of the web interface}
    Firstly, header menu with hyperlinks to each page is located on the top of the interface.
    In the upper left corner of the Control Page there are emotional icon representing facial expressions of the Virtual Assistant
    and text of the VA answers below it.
    In addition, usage manual is provided below VA that can be easily closed by clicking "x" button.
    In the middle of the page, you can find input box with microphone activating and send buttons.
    In order to explain system, there is instruction block under the input box.
    Last but not the least, right hand side of the interface is filled by devices status indicators that shows current statuses.

@@

    As a result, the system sends record of the user input to W3C API and it returns recognised text.

@@

@@

@@

    Text classification is non-trivial complex task that is cannot be solved sequentially
    Artificial neural network systems (ANN) provides the better solution \cite{14}.
    Backpropagation as an ANN is very useful in recognizing complex patterns and performing nontrivial mapping functions.
    The figure below represents a Feed Forward Neural Network (FNN) diagram used in the project.
    The rounded objects represent the artificial neurons.
    The directed lines that are connecting the neurons are called weights that are the multiplication coefficients for input signal.\\

@@

    Topology of the Artificial Neural Network consists of Input, Output and Hidden layers.\\

@@

    As a result, it followed by a squashing nonlinearity.
    While training the ANN it was concluded that the accuracy of the neural network does not significantly changes between one hidden layer neural network and multiple hidden layer neural network.
    The most efficient number of hidden layer neurons (14) was found by calculation of the delta that was calculated by
    1000 iterations of Backpropogation training algorithm with standard training/test set especially created for this experiment.\\

@@

    The system normally does not accept any classification lower that 30\% possibility, and if user says something not
    correlated to the predefined preferences, the system will skip classification and ask again.\\

@@

        User input is: I need to finish my project about flu\\
        System classified it as: [['Work', 0.99951473383654765], ['Health', 0.056650409249493161], ['Entertainment', 0.0011293354032656073], ['Energy', 1.4169164768812246e-05], ['Security', 1.238332260956378e-05], ['Food', 3.1674436013529605e-07]]

@@

    It was used Backpropogation method for the synapses optimisation.

@@

    In order to train neural network, a set of training documents and a specification of the pre-defined categories the
    documents belong to are required.

@@

    The training examples in the training set are then presented to the neural network classifier in random order, and
    the connection weights are adjusted according to the Backpropagation learning rule.
    This process is repeated until the learning error falls below a predefined tolerance level (99.95\%).\\

@@

    Core of the Rule-Based Reasoner is the set of if-else rules.
    Firstly, RBR checks the status of the device and compares it with order.
    Secondly, it checks is there conflict between user command and rule.
    If there is conflict it executes Case-Based Reasoner (CBR).\\

@@

    CBR is the foundation of the many intelligent systems.

@@

    CBR is based on a suggestion that the similar cases have similar solution \cite{7}.\\

@@

    In our case inputs to the system are in different systems of measurements.

@@

    As a result, standard Euclidean Distance cannot be used as a distance measurement algorithm.\\

@@

    Using of Mahalanobis distance significantly increases kNN accuracy \cite{17}.\\
    Based on the data from Rule-Based Reasoner and actions done by the system it sends human readable report or response to user.\\

@@

    In consequence, we developed API to communicate with it that is represented by Device Control Unit in the architecture diagram.

@@

    Sequence diagram of the system can be found in figure below.
    It shows three main scenarios\footnote{Scenario - set of similar cases} inside the system.\\
        \includegraphics[width=\textwidth]{UML.png}
        \caption[]{UML Sequence diagram of the system}
    In order to describe system lifelines, there is explanation of the scenarios.
    First of all, the user sends command to the system (1.1) that is analysed by Dialogue Component (1.2) via Classification ANN (1.3, 1.4).
    Next, system sends classified order to the RBR (1.5) and checks it`s context (1.6 - 1.9).
    If there is no conflict, it changes device status (1.10, 1.11) and answers to the user (1.12 - 1.14).
    Else, it executes Conflict Resolution Scenario by Case-Based Reasoner (2.1).\\
    Next, it informs the user about conflict (2.2 - 2.4) and wait command.
    If the user cancels command (2.5, 2.6), it aborts Conflict Resolution loop.
    Else, the system asks for argumentation (2.7, 2.8) from user (2.9, 2.10) and classifies it (2.11, 2.12).
    After collection of data (2.13) CBR reads old cases (2.14, 2.15) and makes a decision (2.16).\\
    In the settings pages the user changes database (3.1 - 3.4).
    \section{Results and Validation}
    To evaluate the system we have constructed randomised double-blind experiment.
    In order to perform randomized double
    blinded experiment, we developed scenario creating sub-module.
    Firstly, it creates random scenario for tester by choosing
    conflicting device and reasons for tester by using crypto-secure randomise function based on operation system inner
    clocks.
    Secondly, it provides such instructions to testers that he or she was
    asked to provide command and arguments in their own words.
    As a result, scenarios were hidden from us and testers till
    the beginning of the experiment.\\
    In addition, thirteen testers were asked to fill evaluation form.
    In the evaluation form testers were asked to answers questions with quantitative form, where 0 is very badly and 4 is very good, about Speech recognition,
    classification, conflict resolution, total idea, interface design, interaction with VA and user friendliness.
    Furthermore, they were provided with additional text box under each question to justify their answers if they though
    that they need to be justified and one more question about what they would include or change in the system.\\
    The majority of the responses were positive \footnote{83 of 91 quantitative answers are positive, 5 neutral and 3 negative.}
    and the average of the all answers are higher the "Good" level (3 and more) except "Conflict Resolution" question, which
    has 2.9 average value with 1.2 standard deviation amount.
    The basic quantitative analysis of the answers are shown in the figure below.\\
        \includegraphics[width=\textwidth]{eval.png}
        \caption[]{Quantitative analysis of the answers}
    The question about conflict resolution quality was the most hard for the system, because it has two negative answers.
    Firstly, there was disagreement about priorities policy of the system and the general view of the user.
    The tester did not agree that the adult has higher priority with entertainment issue versus younger with work issue.
    The second case was unique and new to the CBR, and it did not managed to give appropriate output.
    Analysis of the system logs and simulation of the case gave us better understanding of the system fault.
    As a result, there is a list of possible cause effects and ways to solve them:\\
        \item Lack of training data: create more training cases and store them into Databases.
        \item Ineffective distance measurement algorithm: replace k-Nearest Neighbor algorithm with Artificial Neural Network or other machine learning algorithm. Combination of heuristic algorithms gives higher results than separately \cite{12}.
        \item Ineffective input matrix: replace input variables by new system that will take into account difference between reasons.
    \section{Conclusion}
    This paper presents Virtual Assistant in the multiple user Smart Home environment.
    The Virtual Assistant was created
    to manage and monitor Smart Home environment by dialogue based interaction with users.
    Different machine learning
    algorithms and cloud technologies were implemented to meet project objectives.
    The main focus of the research was to
    develop adaptive context aware conflict resolution system based on Case-Based Reasoner.
    The validation tests feedback is positive.
    a case to the database of Case-Based Reasoner.
    In order to change paradigm from technology centered perspective to human centered perspective,
    it is significant to introduce behaviour adapting sub-system \cite{2}.\\
    In addition, it is recommended to implement machine learning algorithms to measure distances between cases to
    increase accuracy of the Case-Based Reasoner.\\
    All the materials and sources of the system can be found in the GitHub repository of the project \footnote{https://github.com/BiggyBaron/VirtualAssistant}.
    Furthermore, there is well structured and full observing documentation is available on Wiki page of the system \footnote{https://github.com/BiggyBaron/VirtualAssistant/wiki}.
    \begin{thebibliography}{1}
        \bibitem {1}
        Alirezaie, M., Renoux, J., Köckemann, U., Kristoffersson, A., Karlsson, L., Blomqvist, E., Tsiftes, N., Voigt, T., Loutfi, A.: An Ontology-based Context-aware System for Smart Homes: E-care@home. Sensors. 17, 1586 (2017).

@@

@@
